RNA-seq from 4 cell populations

### 2021-08-03 deconvolution/fans4/molec_profiling.Rmd
bug fix

# cd /hpc/users/hoffmg01/work/cmc_analysis/src
cd /hpc/users/hoffmg01/work/CMC/covarr-de/deconvolution/fans4
# rm -rf molec_profiling_cache/
ml git pandoc
git pull
export OMP_NUM_THREADS=1
R

@@

# Gene set analysis
```{r zenith.celltype, cache=FALSE}
knitr::knit_exit()

>>>>

# cd /hpc/users/hoffmg01/work/cmc_analysis/src
cd /hpc/users/hoffmg01/work/CMC/covarr-de/deconvolution/fans4
# rm -rf molec_profiling_cache/
ml git pandoc
git pull
# export OMP_NUM_THREADS=1
R

@@

# Gene set analysis
```{r zenith.celltype, cache=FALSE}

geneSets_GO = get_GeneOntology("MF")

# Map from Ensembl genes in geneSets_GO to 
# Ensembl names from RNA-seq data 
index = ids2indices( recodeToList(geneSets_GO), rownames(fitBasic))

# filter by size of gene set
n_genes_in = 30
setSize = sapply(index, length)
idxGO = index[(setSize > n_genes_in) & (setSize < 500)]

df_CT_zenith = lapply( colnames(coef(fitBasic)), function(key){
  res = zenith( fitBasic, coef = key, index = idxGO)
  data.table(Geneset = rownames(res), res, coef = key)
})
df_CT_zenith = do.call(rbind, df_CT_zenith)

df_gs = lapply( df_CT_zenith[,unique(coef)], function(key){

  df_CT_zenith[(coef == key),][order(p.greater),][1:4,]
  })
df_gs = do.call(rbind, df_gs)
```

  res = zenith( fitBasic, coef = 'CellTypeGLU', index = idxGO)

```{r eval=FALSE}
# form = ~ CellType + Gender + Batch

# idx = info$CellType %in% c("Olig", "GABA")
# isexpr = filterByExpr(geneCounts[,idx], model.matrix(~CellType, info[idx,]))
# dge = DGEList(geneCounts[isexpr,idx])
# dge = calcNormFactors(dge)
# vobj = voom(dge, model.matrix(~CellType, droplevels(info[idx,])))

# fit = lmFit( vobj, model.matrix(form, droplevels(info[idx,])))
# fit = eBayes(fit)
# fit = dream(vobj, form, info[idx,])
# fit = eBayes(fit)
# res2 = zenith(fit, coef='CellTypeOlig',idxGO )

# # Map from Ensembl genes in geneSets_GO to 
# # Ensembl names from RNA-seq data 
# index = ids2indices( recodeToList(geneSets_GO), rownames(fit))

# n_genes_in = 20
# idxGO = index[sapply(index, length) > n_genes_in]

# res = camera( vobj, idxGO, model.matrix(form, droplevels(info[idx,])), inter.gene.cor=NA, contrast='CellTypeOlig')
